---
title: "Mtcars Data Analysis"
author: "Ji"
date: "2022-11-14"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Function of the app

- This app is used to analyze the mtcars dataset.
- Mpg value is predicted by significant parameters: am, wt and qsec.
- Linear model is used for prediction.

## Data introduction
Mtcars is composed of 32 observations of 11 variables. Among them, am (Transmission), wt (weight), and qsec (1/4 mile time) are significant variables for mpg that have been found in the Regression Models Course.
```{r, echo=FALSE}
data(mtcars)
str(mtcars)
```

## Parameters analysis
- Am = 0 and am = 1 separates the dataset into 2 different linear model.
- Mpg is negatively correlated with wt and qsec.
```{r cars, echo = FALSE}
library(ggplot2)
mtcars$am<-as.factor(mtcars$am)
ggplot(data = mtcars, aes(x=wt, y = mpg,color = am, size = qsec))+
  geom_point()+
  geom_smooth(method= "lm")+
  labs(title = "mpg vs. wt, qsec and am")
```

## Use of the app
- The user selects the Transmission of the car.
- The app shows the linear fit of the data.
- The user uses the slider to set the Wt and Qsec of the car.
- The user's input is shown below the figure together with the predicted Mpg value.
